---
title: "Motor Trend Data"
author: "James Canterbury"
date: "1/22/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, echo = FALSE, 
                      message = FALSE, warning = FALSE)
```

## Introduction

- This project was created as part of the Developing Data Products course of the Coursera [Data Science Specialisation](https://www.coursera.org/specializations/jhu-data-science).

- The goal of the project is to create a web page presentation using R Markdown that features a plot created with Plotly, and to host the resulting web page on either GitHub Pages, RPubs, or NeoCities.

- The interactive plot on the next slide illustraties the relationship between MPG and Horsepower for the Mtcard dataset.
  


```{r prerequisites}
library(dplyr)
library(tibble)
library(plotly)
```


## Motor Trend Mtcars Data : HP and MPG Relationship
```{r load_data, }
mtcars1 <- subset(mtcars, select = c( hp, mpg))




font  <- list(  family = "Arial",   size = 16,  color = "#7f7f7f")
xAxis <- list(  title = "Horsepower",    titlefont = font)
yAxis <- list(  title = "MPG",               titlefont = font)


plotly_plot<-plot_ly(mtcars1, x = ~hp, y= ~mpg ,  type="bar", mode="lines") %>% 
  layout(xaxis = xAxis, yaxis = yAxis
         ,legend= list(x = 1 ,    y = 1 ,  bgcolor = "#F3F3F3" ))

suppressMessages(suppressWarnings(plotly_plot))


```



## Notes

### Source code

- The R Markdown source code of this presentation can be found in [this GitHub repository](https://github.com/JamesCanterbury/coursera-ddp-project3-plotly).


#### Code is also in text form below

mtcars1 <- subset(mtcars, select = c( hp, mpg))




font  <- list(  family = "Arial",   size = 16,  color = "#7f7f7f")
xAxis <- list(  title = "Horsepower",    titlefont = font)
yAxis <- list(  title = "MPG",               titlefont = font)


plotly_plot<-plot_ly(mtcars, x = ~hp, y= ~mpg ,  type="bar", mode="lines") %>% 
  layout(xaxis = xAxis, yaxis = yAxis
         ,legend= list(x = 1 ,    y = 1 ,  bgcolor = "#F3F3F3" ))

suppressMessages(suppressWarnings(plotly_plot))
